The Talking Heads Experiment

### 2015-04-27 chap9/chap9.tex
attended to all todonotes
fixed remaining widows and orphans

N01SE celebrates the essential excess from which information is drawn. It probes many different ways of seeing and 
being in the world. Chances are your own sense of order is already someone else's N01SE.\todo{I have unset italics for this quotation}
\end{quotation}
%\begin{figure}[htbp]
%  \centerline{\includegraphics[width=.95\textwidth]{chap9/figs/latour.pdf}}
%\caption{\label{latour} 
%Luc Steels Discusses The N01SE exhibition with Bruno Latour who intensively followed the experiments already from the first series at the Laboratorium exhibition in Antwerp. His comments significantly improved the initial designs.}
%\end{figure}

@@

{\bf2000-03-08 15:54:17	phlox}\\
{\itshape RE: In t' kingdon of t' blind, t' 1-eyed man is ki}\\
i know who francis crick is. and as he's good mates with luc and angus - they probably gave him admin rights. believe me, he's no hackdemon . . . .	\\

@@

\rule{0.8\textwidth}{.4pt}
\clearpage
{\bfshape 2000-03-08 17:31:27 phlox}\\
{\itshape RE: Phloxy Lady}\\
too right. do it.\\

@@

{\bf2000-03-08 21:03:19	Trash}	\\
{\itshape who is on whos side??}\\
Just a question how you met angus, adam and clive????\\
Second ques... How you get on?? do you do it the same way as us??? \\
(Please email fire-for-effect@hotmail.com with this one!!)\\
Finally to get straight to the point are you one of them??? dun dun dungggggggggggggg \\
Trash (Hull Uni's Commander of Conspiracy Theories)"	\\

@@

{2000-03-08 23:14:10 fish}\\
{\itshape RE: who is on whos side??}\\
{\itshape i am most definitely NOT one of them!}\\

@@

Many aspects of this episode are remarkable, not in the least that those responsable for an 
exhibition (i.c. Denna Jones (i.e. phlox) and ``fish'') were bent on creating a wave of negative reactions and 
destructions against one of the exhibition pieces entrusted to them. Apparently this behaviour was triggered through
a conflict 
with Adam Lowe, curator of the N01SE exhibition, but the team behind the Talking Heads experiment had nothing to do 
with this. Another remarkable fact is that the hacker group 
became aggressive as soon as they felt they were no longer able to have control the way they wanted to, specifically 
to introduce disrespectful language or to subvert agent scripts to circumvent the central scheduler so that they 
could send their agents in priority to the sites of their choosing.
This style of behaviour is a personality trait which is commonly recognised as characteristic for 
hackers, including by members of the hacker community themselves:\footnote{
Raymond, E. (2013) The new hackers dictionary. Available as http://www.catb.org/jargon/html/index.html.}

@@

\begin{enumerate}
\item The {\itshape European Conference on Artificial Life} at the EPFL in Lausanne (Switzerland) in September 1999. 
Papers on computational and robotic 
models of language evolution were (and still are) greeted with hostility at linguistics conferences (even 
conferences on computational linguistics) and they are still routinely rejected for linguistics journals, as 
being irrelevant for understanding more about human language. 
However the Artificial Life conferences and journals welcomed the approach from the beginning. This is 
not surprising because agent-base modeling is one of the main tools used in that field and an evolutionary 
stance is seen as obvious to biologists. The Lausanne conference was organised in line with earlier 
conferences on artificial life, showing work on life-like robots, computer simulations, and new chemically based 
forms of life. It also featured a series of live demos. The portable demonstration of the Talking Heads was part 
of these demonstrations, set up to accompany a presentation at 
the conference by myself and Fr\'{e}deric Kaplan\footnote{
The paper published for this conference is \cite{Steels:1999}.}
It was linked in with the ongoing experiment during Laboratorium in Antwerp. 
\item The {\itshape Neuer Aachener Kunstverein} in Aachen (Germany) in collaboration with the 
RWTH (the technical university of Aachen) organised a general exhibition on modelling called 
Modell-Modell. Within this framework, artist Anne-Mie van Kerckhoven invited me to cooperate in a laboratory on 
language and colour called ``Cyberlabor Chromosophy''. As part of this laboratory, the portable Talking Heads 
experiment was installed and ran from 5 May to 16 June 2000. It featured not only the portable Talking Heads, 
which was demonstrated live, but also posters, talks about the project and additional art works. 
\item The portable Talking Heads was also featured in an exhibition at the {\itshape Ludo Mich Gallery} in Antwerp. This 
exhibition focused on colour again and showed several other pieces related to colour and colour perception. 
It was accompanied by a very well attended gallery talk. 
\end{enumerate}
\begin{figure}[htbp]
  \centerline{\includegraphics[width=.90\textwidth]{chap9/figs/Lausanne.pdf}}
\caption{\label{fig:lausanne}Live installation and demonstration of the Talking Heads experiment at the European Conference on Artificial 
Life in 1999.}
\end{figure}
\begin{figure}[htbp]
  \centerline{\includegraphics[width=.80\textwidth]{chap9/figs/mich-gallery.pdf}}
\caption{\label{fig:mich}Live installation at the gallery of Ludo Mich in Antwerp. There was no white board but different 
small pancartes with possible scenes (see in the middle of the picture). The game was displayed much larger against
the back wall.}
\end{figure}

>>>>

N01SE celebrates the essential excess from which information is drawn. It probes many different ways of seeing and 
being in the world. Chances are your own sense of order is already someone else's N01SE.
\end{quotation}
%\begin{figure}[htbp]
%  \centerline{\includegraphics[width=.95\textwidth]{chap9/figs/latour.pdf}}
%\caption{\label{latour} 
%Luc Steels Discusses The N01SE exhibition with Bruno Latour who intensively followed the experiments already from the first series at the Laboratorium exhibition in Antwerp. His comments significantly improved the initial designs.}
%\end{figure}

@@

{\bfshape 2000-03-08 15:54:17	phlox}\\
{\itshape RE: In t' kingdon of t' blind, t' 1-eyed man is ki}\\
i know who francis crick is. and as he's good mates with luc and angus - they probably gave him admin rights. believe me, he's no hackdemon . . . .	\\

@@

\rule{0.8\textwidth}{.4pt}
\clearpage

{\bfshape 2000-03-08 17:31:27 phlox}\\
{\itshape RE: Phloxy Lady}\\
too right. do it.\\

@@

{\bfseries 2000-03-08 21:03:19	Trash}	\\
{\itshape who is on whos side??}\\
Just a question how you met angus, adam and clive????\\
Second ques... How you get on?? do you do it the same way as us??? \\
(Please email fire-for-effect@hotmail.com with this one!!)\\
Finally to get straight to the point are you one of them??? dun dun dungggggggggggggg \\
Trash (Hull Uni's Commander of Conspiracy Theories)"	\\

@@

{\bfseries 2000-03-08 23:14:10 fish}\\
{\itshape RE: who is on whos side??}\\
{\itshape i am most definitely NOT one of them!}\\

@@

Many aspects of this episode are remarkable, not in the least that those responsable for an 
exhibition (i.c. Denna Jones (i.e. phlox) and ``fish'') were bent on creating a wave of negative reactions and 
destructions against one of the exhibition pieces entrusted to them. Apparently this behaviour was triggered through
a conflict 
with Adam Lowe, curator of the N01SE exhibition, but the team behind the Talking Heads experiment had nothing to do 
with this. Another remarkable fact is that the hacker group 
became aggressive as soon as they felt they were no longer able to have control the way they wanted to, specifically 
to introduce disrespectful language or to subvert agent scripts to circumvent the central scheduler so that they 
could send their agents in priority to the sites of their choosing.
This style of behaviour is a personality trait which is commonly recognised as characteristic for 
hackers, including by members of the hacker community themselves:\footnote{
Raymond, E. (2013) The new hackers dictionary. Available as \url{ http://www.catb.org/jargon/html/index.html}.}

@@

\begin{enumerate}
\item The {\itshape European Conference on Artificial Life} at the EPFL in Lausanne (Switzerland) in September 1999. 
Papers on computational and robotic 
models of language evolution were (and still are) greeted with hostility at linguistics conferences (even 
conferences on computational linguistics) and they are still routinely rejected for linguistics journals, as 
being irrelevant for understanding more about human language. 
However the Artificial Life conferences and journals welcomed the approach from the beginning. This is 
not surprising because agent-base modeling is one of the main tools used in that field and an evolutionary 
stance is seen as obvious to biologists. The Lausanne conference was organised in line with earlier 
conferences on artificial life, showing work on life-like robots, computer simulations, and new chemically based 
forms of life. It also featured a series of live demos. The portable demonstration of the Talking Heads was part 
of these demonstrations, set up to accompany a presentation at 
the conference by myself and Fr\'{e}deric Kaplan\footnote{
The paper published for this conference is \cite{Steels:1999}.}
It was linked in with the ongoing experiment during Laboratorium in Antwerp. 
\item The {\itshape Neuer Aachener Kunstverein} in Aachen (Germany) in collaboration with the 
RWTH (the technical university of Aachen) organised a general exhibition on modelling called 
Modell-Modell. Within this framework, artist Anne-Mie van Kerckhoven invited me to cooperate in a laboratory on 
language and colour called ``Cyberlabor Chromosophy''. As part of this laboratory, the portable Talking Heads 
experiment was installed and ran from 5 May to 16 June 2000. It featured not only the portable Talking Heads, 
which was demonstrated live, but also posters, talks about the project and additional art works. 
\item The portable Talking Heads was also featured in an exhibition at the {\itshape Ludo Mich Gallery} in Antwerp. This 
exhibition focused on colour again and showed several other pieces related to colour and colour perception. 
It was accompanied by a very well attended gallery talk. 
\end{enumerate}
\begin{figure}[t]
  \centerline{\includegraphics[width=.90\textwidth]{chap9/figs/Lausanne.pdf}}
\caption{\label{fig:lausanne}Live installation and demonstration of the Talking Heads experiment at the European Conference on Artificial 
Life in 1999.}
\end{figure}
\begin{figure}[htbp]
  \centerline{\includegraphics[width=.80\textwidth]{chap9/figs/mich-gallery.pdf}}
\caption{\label{fig:mich}Live installation at the gallery of Ludo Mich in Antwerp. There was no white board but different 
small pancartes with possible scenes (see in the middle of the picture). The game was displayed much larger against
the back wall.}
\end{figure}
